### 2019-02-26 sections/language.tex
unevaluated means not in normal form

\label{sub:pretasks}
The grammar in \cref{fig:task-grammar} specifies the syntactic category of \emph{pretasks}.
Pretasks are tasks that have unevaluated subexpressions. \fixme{Alejandro: How do you define unevaluated?}
Each pretask will be discussed in more detail in the following subsections.
We use open symbols ($\Edit, \Enter, \Next, \Xor$) for tasks that require user input, and closed symbols ($\Update, \Then, \Or$) for tasks that can be evaluated without user input.

>>>>

\label{sub:pretasks}
The grammar in \cref{fig:task-grammar} specifies the syntactic category of \emph{pretasks}.
Pretasks are tasks that have unevaluated subexpressions.
This means they are considered to be in normal form for the host language, even if their subexpressions are not in normal form.
Each pretask will be discussed in more detail in the following subsections.
We use open symbols ($\Edit, \Enter, \Next, \Xor$) for tasks that require user input, and closed symbols ($\Update, \Then, \Or$) for tasks that can be evaluated without user input.
